### 2022-06-03 main/paper3.tex
Add files via upload

 \begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{tweet_vol_daily.JPG}
    \caption{Number of messages posted daily on StockTwits.}
    \label{fig:tweet_vol_daily}
\end{figure}

@@

\begin{figure*}[h]
\centering
\includegraphics[width=0.75\textwidth]{stocktwits_screeshot_3march2020.JPG}
\caption{Screenshot of StockTwits as of 3rd March 2020. The first message is labeled as bullish by the user ``satkaru", the two next are unlabeled messages that will be classified using a machine learning classifier and the last message is labeled as bearish by the user ``Etrading''.}
\label{screenshot}
\end{figure*}

@@

\begin{figure*}[h]
\centering
        \begin{subfigure}[b]{0.75\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{preclassif.JPG}
        \end{subfigure}
        \caption{Number of user-labeled messages in each category. There are around 60 million unlabeled messages that we classify using the 30 million user-labeled bullish and bearish messages.} 
        \label{categrepartition-preclassif}
\end{figure*}

@@

        \caption{User summary statistics. Top graph is a log-log histogram of the number of followers per user and the bottom graph shows the log-log histogram of the number of messages posted by users.} 
        \label{fig:data-stocktwits1}
\end{figure*}

@@

\begin{figure*}[]
\centering
\begin{subfigure}{0.75\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{top30tickers.jpg}
        \end{subfigure}
        \quad
        \begin{subfigure}{0.75\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{LogTweetsPerFirm_3.jpg}
        \end{subfigure}
        \caption{Firm summary statistics. Top graph shows the top 30 most discussed tickers on the platform. SPY is the ticker of the S\&P and AAPL is the ticker for Apple. Bottom graph shows the distribution of the number of messages across tickers.} 
        \label{fig:data-stocktwits2}
\end{figure*}

@@

    \includegraphics[width=0.75\textwidth]{Negative rate words.jpg}
   \vspace{0.1cm}
    \caption{Bullish word cloud (top), bearish word cloud (bottom). These correspond to the most frequent terms (up to 3-grams) in user-labeled bullish (bearish) messages relative to their total appearance. The size of the terms represent their importance in the cloud.}
    \label{wordclouds}
  \end{center}
\end{figure}

@@

\begin{table}[H]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
\hline \multicolumn{2}{l}{After preprocessing}               \\   \hline \hline                                                                       
(1) & contango still long good            \\
(2) & take profit while you still can \\
(3) & go time boy and girl hold overnight again                                                                  \\
(4) & nice upgrade as company go into its quiet period     \\ 
(5) & market will not reverse again towards closing get put options \\ \hline                                          
\end{tabular*}
\caption{Preprocessing of five sample messages. Preprocessing operations include: punctuation removal, lower casing, apostrophe handling, contraction form handling (i.e. ``won't" becomes ``will not"), tickers removal, users removal, URLs removal, parsing and a simple spell corrector dealing with more than two repeated characters (i.e. ``goooood" becomes ``good")}
\label{tab:preprocess}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{preclassif_acrosstime.JPG}
    \caption{Proportions of user-labeled messages in each category: bullish (green), bearish (red), and unlabeled (gray). Proportions are aggregated monthly.}
    \label{fig:ts_neutral_vs_uncl}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{optimal thresholds.JPG}
    \caption{Optimal classification thresholds. The green (red) line is the F1 score for the bullish versus non-bullish (bearish versus non-bearish) classification, respectively. Circles indicate the maximal F1 scores, along with the corresponding classification score thresholds.}
    \label{fig:optimal_thresholds}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{postclassif_acrosstime3.JPG}
    \caption{Proportions of classified messages in each category: bullish (light green predicted, green user-labeled), bearish (light red predicted, red user-labeled), and neutral (gray). Proportions are aggregated monthly.}
    \label{fig:postclassif_acrosstime}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{spy_vs_marketpol.JPG}
    \caption{Market polarity on the y-axis versus the polarity of the SPY on the x-axis. The red line shows the linear regression line and coefficients.}
    \label{fig:marketpolspy}
\end{figure}

@@

\begin{table}[]
\centering
\begin{tabular}{l|c|c|c|c|c}
                     & $R_{i,t}$ & $R_{i,t}$   & $R_{i,t+1}$ & $R_{i,t+1}$        \\ \toprule 
Constant             & -0.0047*** & -7.92e-05   & -0.0002    & 7e-06         \\
                     & (0.000)    & (9.81e-05)  & (0.000)    & (9e-05)       \\
$P_{i,t}$           & 0.009***   &               & 0.0003     &               \\
                     & (0.000)    &               & (0.000)    &               \\
$CAP_{i,5}$         &            & 0.0007***     &            & -0.0002       \\
                     &            & (0.000)       &            & (0.000)       \\ \bottomrule
$R^2$                & 0.012      & 0.000         & 0.000      & 0.000              \\
No. Obs.             & 34100      & 34024         & 34100      & 34024             
\end{tabular}
\caption{Results from linear regressions of contemporaneous and next period stock returns on polarity. Stock returns are trimmed at the 5\% percentile on both sides. Standard errors are reported in parentheses. Statistical significance at the 99\%, 95\%, and 90\% level is indicated with ***, **, *, respectively.}
\label{regpolret}
\end{table}

\begin{figure*}[]
        \centering
        \begin{subfigure}[b]{0.48\textwidth}
            \centering
            \includegraphics[width=\textwidth]{ts_pol_ret_aapl.JPG}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_amzn.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_tsla.JPG}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_spy.JPG}
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_amd.JPG}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_fb.JPG}
        \end{subfigure}
        \caption{Time series of daily polarity (red - left axis) and daily stock returns (blue - right axis) since 1st of January 2019 for the top 6 most discussed tickers. Pearson correlation between the two time series is shown in the title.} 
        \label{fig:ts}
    \end{figure*}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{timeline.JPG}
    \caption{Timeline of our event studies. $\tau$ is an event date, the event window has 41 business days centered around the event date and the estimation window is a one-year rolling period prior the event.}
    \label{fig:timeline}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{activity-volume.jpg}
    \caption{Changes in weekly volume of transactions on the y-axis versus changes in message activity on the x-axis. Activity is measured in weekly messages posted per firm.}
    \label{fig:actvol}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{abnpol_distr_all.JPG}
    \caption{Empirical distribution of abnormal polarities. Red dashed lines show the one-third and two-third percentiles.}
    \label{fig:abnpol_all}
\end{figure}

@@

\begin{figure}[]
    \centering
    \includegraphics[width=0.75\textwidth]{activity_aapl.JPG}
    \caption{Daily message volume for Apple. Events are days with an unusual high number of messages. Green upper-triangles show bullish events, gray circles are neutral events and red down-triangles represent bearish events.}
    \label{fig:activityaapl}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{caar.JPG}
    \caption{Cumulative average abnormal returns around identified events. CAAR related to bearish, neutral and bullish events are displayed with the red, gray and green line, respectively. Areas around lines show confidence intervals at the 95\% level.}
    \label{fig:ES_CAAR_MM}
\end{figure}

@@

\begin{figure}[]
    \centering
    \includegraphics[width=0.75\textwidth]{caap.JPG}
    \caption{Cumulative average abnormal polarity around identified events. CAAP related to bearish, neutral and bullish events are displayed with the red, gray and green line, respectively. Areas around lines show confidence intervals at the 95\% level.}
    \label{fig:ES_cum_abn_pol_MM}
\end{figure}

\begin{figure*}[]
        \centering
        \begin{subfigure}[b]{0.42\textwidth}
            \centering
            \includegraphics[width=\textwidth]{box_car_t-5.JPG}
            \caption*{CAR 5 days before the event}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{box_cap_t-5.JPG}
            \caption*{CAP 5 days before the event}  
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_car_t.JPG}
            \caption*{CAR on the event date}   
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_cap_t.JPG}
            \caption*{CAP on the event date}   
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_car_t+5.JPG}
            \caption*{CAR 5 days after the event}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_cap_t+5.JPG}
            \caption*{CAP 5 days after the event}  
        \end{subfigure}
        \caption{Distributions of CAP and CAR 5 days before an event, on event date and 5 days after an event. The line inside a box shows the median while the edges of each box represent the 25\% and 75\% quantile of the distribution. From the edges of a box, a distance of 1.5 times the interquartile range is measured and a whisker is drawn up to the largest and lowest observed point from the data that falls within this distance.} 
        \label{fig:boxplotcaar}
    \end{figure*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multicolumn{6}{|c|}{CAR}                                                                                                                                    \\ \hline 
\multicolumn{1}{|l|}{}                     & Alternative Hypothesis                                                         & U     & Z        & $n_1$ & $n_2$ \\ \hline
\multicolumn{1}{|l|}{\multirow{2}{*}{$\tau$-5}} & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 61109 & -1.70    & 452  & 292  \\
\multicolumn{1}{|l|}{}                     & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 54168 & -0.52    & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$}                         & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 50967 & -5.25*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 43100 & -4.96*** & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$+5}                       & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 52738 & -4.63*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 43239 & -4.91*** & 292  & 380  \\ \hline \hline
\multicolumn{6}{|c|}{CAP}                                                                                                                                    \\ \hline
\multicolumn{1}{|l|}{}                     & Alternative Hypothesis                                                         & U     & Z        & $n_1$ & $n_2$ \\ \hline
\multicolumn{1}{|l|}{\multirow{2}{*}{$\tau$-5}} & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 55408 & -3.70*** & 452  & 292  \\
\multicolumn{1}{|l|}{}                     & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 47998 & -3.00***   & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$}                         & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 49385 & -8.98*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 42101 & -5.36*** & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$+5}                       & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 44364 & -7.55*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 40515 & -6.00*** & 292  & 380  \\ \hline
\end{tabular}
\caption{Mann-Whitney U-test estimates for pairwise significant differences between distribution medians. Under the null hypothesis, the two samples represent two distributions with equal median values. Statistical significance at the 99\%, 95\%, and 90\% level is indicated with ***, **, *, respectively.}
\label{utest_res}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cross_sectional_cap.jpg}
    \caption{Cross-sectional statistics of $CAP^{(R)}$. The blue lines shows the cross-sectional mean of the CAP across the 19 tickers over the year. The green and red lines show the up and down 99\% confidence band. We use them as up and down thresholds for the portfolio construction. }
    \label{fig:cross-sec stats}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cumulative_log_return.jpg}
    \caption{Cumulative log returns of both portfolios (x=2.58) and the S\&P500.}
    \label{fig:cumretpf}
\end{figure}

\begin{figure*}[]
        \centering
        %\begin{subfigure}[b]{0.42\textwidth}
        %    \centering
        %    \includegraphics[width=\textwidth]{boxplot.JPG%}
        %    \caption*{Distribution of returns}
        %\end{subfigure}
        %\quad
        %\begin{subfigure}[b]{0.42\textwidth}  
        %    \centering 
        %    \includegraphics[width=\textwidth]{boxplot_zoo%med.JPG}
        %    \caption*{Distribution of returns - zoomed}  
        %\end{subfigure}
        %\vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{distribution_long_positions.JPG}
            \caption*{Number of positions - Long portfolio}   
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{distribution_short_positions.JPG}
            \caption*{Number of positions - Short portfolio}   
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{positions.JPG}
            \caption*{Number of positions over time}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{returns.JPG}
            \caption*{Daily returns}  
        \end{subfigure}
        \caption{Long and Short portfolio for x=2.58.} 
        \label{fig:pf}
    \end{figure*}

>>>>

 \begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{tweet_vol_daily.JPG}
    \mycaption{Number of messages posted daily on StockTwits.}{}
    \label{fig:tweet_vol_daily}
\end{figure}

@@

\begin{figure*}[h]
\centering
\includegraphics[width=0.75\textwidth]{stocktwits_screeshot_3march2020.JPG}
\mycaption{Screenshot of StockTwits as of 3rd March 2020.}{The first message is labeled as bullish by the user ``satkaru", the two next are unlabeled messages that will be classified using a machine learning classifier and the last message is labeled as bearish by the user ``Etrading''.}
\label{screenshot}
\end{figure*}

@@

\begin{figure*}[h]
\centering
        \begin{subfigure}[b]{0.75\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{preclassif.JPG}
        \end{subfigure}
        \mycaption{Number of user-labeled messages in each category.}{There are around 60 million unlabeled messages that we classify using the 30 million user-labeled bullish and bearish messages.} 
        \label{categrepartition-preclassif}
\end{figure*}

@@

        \mycaption{User summary statistics.}{Top graph is a log-log histogram of the number of followers per user and the bottom graph shows the log-log histogram of the number of messages posted by users.} 
        \label{fig:data-stocktwits1}
\end{figure*}

@@

\begin{figure*}[]
\centering
\begin{subfigure}{0.75\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{top30tickers.jpg}
        \end{subfigure}
        \quad
        \begin{subfigure}{0.75\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{LogTweetsPerFirm_3.jpg}
        \end{subfigure}
        \mycaption{Firm summary statistics.}{Top graph shows the top 30 most discussed tickers on the platform. SPY is the ticker of the S\&P and AAPL is the ticker for Apple. Bottom graph shows the distribution of the number of messages across tickers.} 
        \label{fig:data-stocktwits2}
\end{figure*}

@@

    \includegraphics[width=0.75\textwidth]{Negative rate words.jpg}
   \vspace{0.1cm}
    \mycaption{Bullish and bearish word clouds.}{Bullish word cloud (top), bearish word cloud (bottom). These correspond to the most frequent terms (up to 3-grams) in user-labeled bullish (bearish) messages relative to their total appearance. The size of the terms represent their importance in the cloud.}
    \label{wordclouds}
  \end{center}
\end{figure}

@@

\begin{table}[H]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
\hline \multicolumn{2}{l}{After preprocessing}               \\   \hline \hline                                                                       
(1) & contango still long good            \\
(2) & take profit while you still can \\
(3) & go time boy and girl hold overnight again                                                                  \\
(4) & nice upgrade as company go into its quiet period     \\ 
(5) & market will not reverse again towards closing get put options \\ \hline                                          
\end{tabular*}
\mycaption{Preprocessing of five sample messages.}{Preprocessing operations include: punctuation removal, lower casing, apostrophe handling, contraction form handling (i.e. ``won't" becomes ``will not"), tickers removal, users removal, URLs removal, parsing and a simple spell corrector dealing with more than two repeated characters (i.e. ``goooood" becomes ``good")}
\label{tab:preprocess}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{preclassif_acrosstime.JPG}
    \mycaption{Proportions of user-labeled messages in each category}{Proportions of user-labeled messages in each category: bullish (green), bearish (red), and unlabeled (gray). Proportions are aggregated monthly.}
    \label{fig:ts_neutral_vs_uncl}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{optimal thresholds.JPG}
    \mycaption{Optimal classification thresholds.}{The green (red) line is the F1 score for the bullish versus non-bullish (bearish versus non-bearish) classification, respectively. Circles indicate the maximal F1 scores, along with the corresponding classification score thresholds.}
    \label{fig:optimal_thresholds}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{postclassif_acrosstime3.JPG}
    \mycaption{Proportions of classified messages in each category}{Bullish (light green predicted, green user-labeled), bearish (light red predicted, red user-labeled), and neutral (gray). Proportions are aggregated monthly.}
    \label{fig:postclassif_acrosstime}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{spy_vs_marketpol.JPG}
    \mycaption{Market polarity versus the SPY polarity.}{Market polarity on the y-axis versus the polarity of the SPY on the x-axis. The red line shows the linear regression line and coefficients.}
    \label{fig:marketpolspy}
\end{figure}

@@

\begin{table}[]
\centering
\begin{tabular}{l|c|c|c|c|c}
                     & $R_{i,t}$ & $R_{i,t}$   & $R_{i,t+1}$ & $R_{i,t+1}$        \\ \toprule 
Constant             & -0.0047*** & -7.92e-05   & -0.0002    & 7e-06         \\
                     & (0.000)    & (9.81e-05)  & (0.000)    & (9e-05)       \\
$P_{i,t}$           & 0.009***   &               & 0.0003     &               \\
                     & (0.000)    &               & (0.000)    &               \\
$CAP_{i,5}$         &            & 0.0007***     &            & -0.0002       \\
                     &            & (0.000)       &            & (0.000)       \\ \bottomrule
$R^2$                & 0.012      & 0.000         & 0.000      & 0.000              \\
No. Obs.             & 34100      & 34024         & 34100      & 34024             
\end{tabular}
\mycaption{Linear regressions }{Results from linear regressions of contemporaneous and next period stock returns on polarity. Stock returns are trimmed at the 5\% percentile on both sides. Standard errors are reported in parentheses. Statistical significance at the 99\%, 95\%, and 90\% level is indicated with ***, **, *, respectively.}
\label{regpolret}
\end{table}

\begin{figure*}[]
        \centering
        \begin{subfigure}[b]{0.48\textwidth}
            \centering
            \includegraphics[width=\textwidth]{ts_pol_ret_aapl.JPG}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_amzn.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_tsla.JPG}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_spy.JPG}
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_amd.JPG}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{ts_pol_ret_fb.JPG}
        \end{subfigure}
        \mycaption{Time series of daily polarity}{Time series of daily polarity  (red - left axis) and daily stock returns (blue - right axis) since 1st of January 2019 for the top 6 most discussed tickers. Pearson correlation between the two time series is shown in the title.} 
        \label{fig:ts}
    \end{figure*}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{timeline.JPG}
    \mycaption{Timeline of our event studies.}{$\tau$ is an event date, the event window has 41 business days centered around the event date and the estimation window is a one-year rolling period prior the event.}
    \label{fig:timeline}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{activity-volume.jpg}
    \mycaption{Volume of transactions and message activity.}{Changes in weekly volume of transactions on the y-axis versus changes in message activity on the x-axis. Activity is measured in weekly messages posted per firm.}
    \label{fig:actvol}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{abnpol_distr_all.JPG}
    \mycaption{Empirical distribution of abnormal polarities.}{Red dashed lines show the one-third and two-third percentiles.}
    \label{fig:abnpol_all}
\end{figure}

@@

\begin{figure}[]
    \centering
    \includegraphics[width=0.75\textwidth]{activity_aapl.JPG}
    \mycaption{Daily message volume for Apple.}{Events are days with an unusual high number of messages. Green upper-triangles show bullish events, gray circles are neutral events and red down-triangles represent bearish events.}
    \label{fig:activityaapl}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\textwidth]{caar.JPG}
    \mycaption{Cumulative average abnormal returns around identified events.}{CAAR related to bearish, neutral and bullish events are displayed with the red, gray and green line, respectively. Areas around lines show confidence intervals at the 95\% level.}
    \label{fig:ES_CAAR_MM}
\end{figure}

@@

\begin{figure}[]
    \centering
    \includegraphics[width=0.75\textwidth]{caap.JPG}
    \mycaption{Cumulative average abnormal polarity around identified events.}{CAAP related to bearish, neutral and bullish events are displayed with the red, gray and green line, respectively. Areas around lines show confidence intervals at the 95\% level.}
    \label{fig:ES_cum_abn_pol_MM}
\end{figure}

\begin{figure*}[]
        \centering
        \begin{subfigure}[b]{0.42\textwidth}
            \centering
            \includegraphics[width=\textwidth]{box_car_t-5.JPG}
            \caption*{CAR 5 days before the event}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{box_cap_t-5.JPG}
            \caption*{CAP 5 days before the event}  
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_car_t.JPG}
            \caption*{CAR on the event date}   
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_cap_t.JPG}
            \caption*{CAP on the event date}   
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_car_t+5.JPG}
            \caption*{CAR 5 days after the event}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{box_cap_t+5.JPG}
            \caption*{CAP 5 days after the event}  
        \end{subfigure}
        \mycaption{Distributions of CAP and CAR}{Distributions of CAP and CAR 5 days before an event, on event date and 5 days after an event. The line inside a box shows the median while the edges of each box represent the 25\% and 75\% quantile of the distribution. From the edges of a box, a distance of 1.5 times the interquartile range is measured and a whisker is drawn up to the largest and lowest observed point from the data that falls within this distance.} 
        \label{fig:boxplotcaar}
    \end{figure*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multicolumn{6}{|c|}{CAR}                                                                                                                                    \\ \hline 
\multicolumn{1}{|l|}{}                     & Alternative Hypothesis                                                         & U     & Z        & $n_1$ & $n_2$ \\ \hline
\multicolumn{1}{|l|}{\multirow{2}{*}{$\tau$-5}} & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 61109 & -1.70    & 452  & 292  \\
\multicolumn{1}{|l|}{}                     & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 54168 & -0.52    & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$}                         & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 50967 & -5.25*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 43100 & -4.96*** & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$+5}                       & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 52738 & -4.63*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 43239 & -4.91*** & 292  & 380  \\ \hline \hline
\multicolumn{6}{|c|}{CAP}                                                                                                                                    \\ \hline
\multicolumn{1}{|l|}{}                     & Alternative Hypothesis                                                         & U     & Z        & $n_1$ & $n_2$ \\ \hline
\multicolumn{1}{|l|}{\multirow{2}{*}{$\tau$-5}} & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 55408 & -3.70*** & 452  & 292  \\
\multicolumn{1}{|l|}{}                     & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 47998 & -3.00***   & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$}                         & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 49385 & -8.98*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 42101 & -5.36*** & 292  & 380  \\ \hline
\multirow{2}{*}{$\tau$+5}                       & $H_1$ : $\theta_{bullish} > \theta_{neutral}$ & 44364 & -7.55*** & 452  & 292  \\
                                           & $H_1$ : $\theta_{neutral} > \theta_{bearish}$  & 40515 & -6.00*** & 292  & 380  \\ \hline
\end{tabular}
\mycaption{Mann-Whitney U-test estimates}{Mann-Whitney U-test estimates for pairwise significant differences between distribution medians. Under the null hypothesis, the two samples represent two distributions with equal median values. Statistical significance at the 99\%, 95\%, and 90\% level is indicated with ***, **, *, respectively.}
\label{utest_res}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cross_sectional_cap.jpg}
    \mycaption{Cross-sectional statistics of $CAP^{(R)}$.}{The blue lines shows the cross-sectional mean of the CAP across the 19 tickers over the year. The green and red lines show the up and down 99\% confidence band. We use them as up and down thresholds for the portfolio construction. }
    \label{fig:cross-sec stats}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cumulative_log_return.jpg}
    \mycaption{Cumulative log returns of both portfolios (x=2.58) and the S\&P500.}{}
    \label{fig:cumretpf}
\end{figure}

\begin{figure*}[]
        \centering
        %\begin{subfigure}[b]{0.42\textwidth}
        %    \centering
        %    \includegraphics[width=\textwidth]{boxplot.JPG%}
        %    \caption*{Distribution of returns}
        %\end{subfigure}
        %\quad
        %\begin{subfigure}[b]{0.42\textwidth}  
        %    \centering 
        %    \includegraphics[width=\textwidth]{boxplot_zoo%med.JPG}
        %    \caption*{Distribution of returns - zoomed}  
        %\end{subfigure}
        %\vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{distribution_long_positions.JPG}
            \caption*{Number of positions - Long portfolio}   
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{distribution_short_positions.JPG}
            \caption*{Number of positions - Short portfolio}   
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{positions.JPG}
            \caption*{Number of positions over time}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.42\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{returns.JPG}
            \caption*{Daily returns}  
        \end{subfigure}
        \mycaption{Long and Short portfolios for x=2.58.}{}
        \label{fig:pf}
    \end{figure*}
